---
title: "R Markdown & Plotly"
author: "Grzegorz Olszewski"
date: "7 kwietnia 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(plotly)
library(dplyr)
```

## Introduction

For this presentation I used some dataset from Kaggle competition Titanic Disaster.
This dataset contains:

- Survival (1 - Yes, 0 - No)
- Pclass - class of room
- Age
- Sex
- Sinsp - number of siblings/spouses aboard of Titanic
- Parch - number of parents/childrens aboard of Titanic
- Fare - passenger fare


## Some explanatory plots


```{r plotly }
df <- read.csv("train.csv")

plotly::plot_ly(df, x=~Sex, y=~Age, type = "box") %>% 
  layout(title = "Age and Sex of passengers")

df %>% 
  group_by(Pclass) %>% 
  summarise(Survived = mean(Survived)) %>% 
  plot_ly(x=~Pclass, y=~Survived, type = "bar") %>% 
  layout(title = "% of survived by class room")

```

## Other chart



```{r fare}
df %>% 
  plot_ly(x=~Survived, y=~Fare, type = "box") %>% 
  layout(title ="Survived by fare cost")
```

## Conclusions

As we can see type of room (quality) and also fare cost influence very much on probability of survive from Titanic Disaster.



